\chapter*{Acknowledgements}
% parents
First of all, I would like to thank my parents P.Y. and H.K. Liang for the love, guidance and support they have shown me in every step of my life.
I would also like to thank my brother Chuen Tschi and other family members for being there for me when I needed.

Thanks to my thesis advisors Damien Pellier, Humbert Fiorino, and Prof. Sylvie Pesty for their supervision and guidance, as well as my former and current colleagues in the HAwAI (formerly MAGMA) team for their support throughout the thesis.
My sincere gratitude also goes to Nadine Mandran, who was always happy to help me with my user experiments and provided me with essential feedback on both the design and the write-up.
Similarly, I would like to thank other members of the lab and former interns that I worked with and that helped me with any aspects for my thesis.

% PhD advisor Pierre geneves 
I am also grateful to my advisor from école doctoral Dr. Pierre Genevès for providing an outside perspective and my external advisor Prof. Dominique Duhaut for believing in me.
I still remember the time when I just finished my Master thesis presentation in 2016, Dominique told me ``Someone like you should do a Ph.D." - and so I did.
Also thanks to the \textit{rapporteurs} Rachid Alami and Olivier Ly for their time and feedback to my thesis.

%Justin Huang
I would like to express my sincere gratitude to Maya Cakmak and the Human-Centered Robotics Lab, for inviting me to work with her for 5 months of my Ph.D.
%It was truly one of the most fun and inspiring experiences for me to continue work in robotics research after my thesis.
I would also like to thank my friends in Grenoble, Seattle, London, and anywhere else in the world who supported me throughout my thesis.
%Finally, I would like to thank my former boss John Hayes, who always asked me the unconventional question ``Is this really what you want to do?" and encouraged me to follow my interests which finally led to me doing this thesis.

%To the rest, \ie all people whose names start with a French alcoholic beverage, \eg vin, and end with a currency, \eg cent, I would like to NOT thank you for NOTHING because you simply suck.